\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2011-05-09 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
added/documented MSnSet purity correction method
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@55356 bc3139a8-67e5-0310-9ffc-ced21a209358

>>>>

\subsection{Purity correction}
\label{sec:purcor}

Impurities in the reporter reagents can bias the results and can be corrected when 
manufacturers provide correction coefficients. 
These generally come as percentages of each reporter ion that have masses differing 
by -2, -1, +1 and +2 Da from the nominal reporter ion mass due to isotopic variants.  
The \Rfunction{purityCorrect} method applies such correction to \Robject{MSnSet} 
instances. It also requires a square matric as second argument, \Robject{impurities}, 
that defines the repaltive percentage of reporter in the quantified each peak. 
See \texttt{?purityCorrect} for more details.

<<purityCorrect,echo=TRUE,cache=FALSE>>=
impurities <- matrix(c(0.929,0.059,0.002,0.000,
                       0.020,0.923,0.056,0.001,
                       0.000,0.030,0.924,0.045,
                       0.000,0.001,0.040,0.923),
                     nrow=4)
qnt2.crct <- purityCorrect(qnt2,impurities)
head(exprs(qnt2))
head(exprs(qnt2.crct))
@
